Dynamical Properties of Molecular-forming Gas Clumps in Galaxies at the Epoch of Reionization

### 2020-04-18 WRITEUP/ms_referee2.tex
round 2

The simulation zooms in on a galaxy named after the flower \flower, whose properties are given in \citet{Pallottini17a} and are briefly summarized in the following. \flower is a Lyman-break galaxy that at $z\simeq 6$ is hosted by a dark matter halo of mass
{\bf $M_{\rm DM}\simeq$\eq3.5\,$\times$\,10$^{11}$\,\Msun} at the center of a cosmic web knot, and accretes mass from the IGM mainly via three filaments of length $\simeq$\,100\,kpc. \flower has a stellar mass of {\bf $M_\star\simeq$\,2.6\E{10}\,\Msun}, a metallicity of $Z\simeq$\,0.5\,$Z_{\odot}$, a molecular gas mass of $M_{\rm H2}\simeq$\,5\E{7}\,\Msun, and a SFR of 30\,--\,80\,\Msun\,yr\pmOne.
%
The specific SFR of \flower is ${\rm sSFR} \equiv {\rm SFR}/M_{\star} \simeq$~4--40 ~Gyr\pmOne, compatible with the sSFR vs.\ $M_{\star}$ relation observed at high redshift \citep{Jiang16a}. The effective stellar radius of \flower is $\simeq$\,0.5\,kpc and the dark matter virial radius is $r_{\rm 200}\simeq$\,15\,kpc.
{\bf The stellar-to-halo mass ratio of \flower is $M_\star/M_{\rm DM}\,\simeq\,$0.07.
Abundance matching of halos shows that this ratio varies as the halo mass becomes much larger or smaller than from $M_h$\ssim10$^{12}$\,\Msun (see \citealt{Moster13a, Behroozi13b, Behroozi15a, Moster18a}). The ratio of \flower is higher than e.g., \citet{Katz17a}  and \citet{Ceverino17a} which could be a result of different feedback implementation.
}

@@

>>>>

The simulation zooms in on a galaxy named after the flower \flower, whose properties are given in \citet{Pallottini17a} and are briefly summarized in the following. \flower is a Lyman-break galaxy that at $z\simeq 6$ is hosted by a dark matter halo of mass
{\bf $M_{\rm DM}\simeq$\eq3.5\,$\times$\,10$^{11}$\,\Msun} at the center of a cosmic web knot, and accretes mass from the IGM mainly via three filaments of length $\simeq$\,100\,kpc. \flower has a stellar mass of {\bf $M_\star\simeq$\,2.6\E{10}\,\Msun}, a metallicity of $Z\simeq$\,0.5\,$Z_{\odot}$, a molecular gas mass of $M_{\rm H2}\simeq$\,5\E{7}\,\Msun, and a SFR of 30\,--\,80\,\Msun\,yr\pmOne.
%
The specific SFR of \flower is ${\rm sSFR} \equiv {\rm SFR}/M_{\star} \simeq$~4--40 ~Gyr\pmOne, compatible with the sSFR vs.\ $M_{\star}$ relation observed at high redshift \citep{Jiang16a}. The effective stellar radius of \flower is $\simeq$\,0.5\,kpc and the dark matter virial radius is $r_{\rm 200}\simeq$\,15\,kpc.
{\bf The stellar-to-halo mass ratio of \flower is $M_\star/M_{\rm DM}\,\simeq\,$0.07.
Abundance matching of halos shows that this ratio varies as the halo mass becomes much larger or smaller than from $M_h$\ssim10$^{12}$\,\Msun 
(see \citealt{Moster13a, Behroozi13b, Behroozi15a, Moster18a})\footnote{The stellar mass-to-halo mass ratio for Althaea at $z$\eq6 is about 0.07. 
This is a factor of about 3 higher than the typical value inferred by abundance matching models, that typically gives $\sim0.02$. 
Note however that the ratio from abundance matching can vary; for instance, \citet{Behroozi13b} (main method) finds a ratio of 0.015\,--\,0.025 
is for a halo mass between $M_{\rm halo}$\ssim10$^{10.5}$--$10^{12}$\,\Msun, whereas in the same paper the authors find 
0.01--0.05 in the same mass range from direct abundance matching 
(see the Appendix therein). 
Additionally, from an earlier abundance matching study, \citet{Moster13a} find a ratio 0.005, i.e., within a factor 3 from \citet{Behroozi13b}.}. 
The ratio of \flower is higher than e.g., \citet{Katz17a}  and \citet{Ceverino17a} which could be a result of different feedback implementation.
}

@@

{\bf As seen in \Sec{dist}, the cuts used to identify the molecular structures are based on the H$_2$ number density, which ranges from 
n$_{\rm H2}$\ssim0.1\,--\,30\,\cc. We do not explicitly use a minimum H$_2$ fraction to select the structures. 
Among the various cuts, two physical regimes are identified, corresponding to materials in the disk/interarm material and MGCs (see Fig. 5). 
The former with n$_{\rm gas}<100$\,\cc and n$_{\rm H2} < 5$\,\cc, whereas the latter with 
n$_{\rm gas}$\ssim$100$\,\cc and n$_{\rm H2} \gtrsim10$\,\cc (see also Fig. 5 of \citet{Pallottini17b} 
for details\footnote{In particular, with their analysis of the Minkowski function of the molecular density field (see Fig. 6 therein)}). 
Considering that $f_{\rm H2}$\eq$\rho_{\rm H2} / \rho_{\rm H,total}$\eq$\rho_{\rm H2}/(\mu \rho_{\rm gas})$\eq
$m_{\rm H2} n_{\rm H2} / m_p~\mu~n_{\rm gas}$\ssim2 $n_{\rm H2}/(0.7~n_{\rm gas})$, 
for the disk/interarm, $f_{\rm H2}$\ssim14\% and for the MCCs, $f_{\rm H2}$\ssim28\%. 
Note that for the lowest value of the H2 cuts, this fraction might be lower; however, 
removing regions selected with such cuts yields no qualitative change to the physical interpretation resulting from the analysis.}
